SDR enhancement by clouds

### 2024-03-19 article/article.tex
Commit 2024-03-19 17:16
Commit 2024-03-19 19:27

In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies form instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

To preserve an unbiased representation of the data we applied a constrain similar
the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including night time near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than \(78^\circ\).

@@

We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the the TSI provided by
NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA. For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw). Thus, the modeled GHI\_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one minute measurements.
The annual mean over irradiance is
\(0.23\pm 0.11\,W/m^2\)
(Figure~\ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/relative_distributions-4}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-9}
\end{figure}

>>>>

In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

To preserve an unbiased representation of the data we applied a constraint similar
the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including nighttime near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than \(78^\circ\).

@@

We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to model
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the TSI provided by
NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA. For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw). Thus, the modeled GHI\_modeled we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

@@

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.
The annual mean over irradiance is
\(0.23\pm 0.11\,W/m^2\)
(Figure~\ref{fig:P-energy-mean}),
but this value is not very useful due the high
variability of this metric.

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P-relative-distribution-diff-1}

@@

\caption{Distribution of CE over irradiance}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-10}
\end{figure}
